The Numerical Accuracy of Computing Electrostatic Interaction in the Inhomogeneous and Correlated Molecular Systems: for the Ewald Summation, SPME and Staggered Mesh Ewald Methods.

### 2012-07-13 longRange.hetero/alltext/publish/resubmit/lett.tex
delete figure, fix bug in letter

In the revised manuscript,
we consider both of the two types of the correlations:
(1) the bonded correlation
that originates from the rigid H-O
bond and H-O-H angle within one molecule,
and (2) the
non-bonded correlation or the
intermolecular correlation that originates from
a complex coupling of various intermolecular interaction.
Estimates for the bonded correlation
have already been developed by the old manuscript,
while the non-bonded estimate
is newly added according to the reviewers' suggestion.
Please note that
both the bonded and non-bonded nearest neighbor approximations
require some uniformity of the correlation in the system:
the bonded estimate requires the uniformity of the water
direction preference (as has been discussed in the old manuscript),
while the non-bonded estimate requires the uniformity
of the density distribution and the isotropicity of the system.
Otherwise the cost of the error estimate would be $\mathcal O(N^2\log N)$.
For the non-bonded correlation,  the nearest neighbor approximation 
is expressed in terms of the radial distribution
functions (RDFs), see the new Eq. (21) and (22). In example 3, a global RDF is not well defined,
so we calculated the RDF and nearest neighbor approximation
only for the liquid phase, see the dotted line in Fig.7. By adding
the non-bonded correlation, the quality of the error estimate
is further improved.
Also the convergence with respect to
the neighboring range $R_g$ is investigated, see Fig.8.
Relavant changes to the manuscript
have been made on page 9,
11 (4-th line from the bottom), 12, 29 (12-th line). All changes are marked 
in red for convenience.
\\

@@

In the revised manuscript, the correlation error are considered
in two types: 
(1) the bonded correlation
that originates from the rigid H-O
bond and H-O-H angle within one molecule,
and (2) the
non-bonded correlation or the
intermolecular correlation that originates from
a complex coupling of various intermolecular interaction.
Estimates for the bonded correlation
have already been developed by the old manuscript,
while the non-bonded estimate
is newly developed according to the reviewers' suggestion.
Please note that
both the bonded and non-bonded nearest neighbor approximations
require some uniformity of the correlation in the system:
the bonded estimate requires the uniformity of the water
direction preference (as has been discussed in the old manuscript),
while the non-bonded estimate requires the uniformity
of the density distribution and the isotropicity of the system, which
are also the prerequisites for reducing $\rho^{(2)}$ to $g(r)$.
Otherwise the cost of the error estimate would be $\mathcal O(N^2\log N)$.
For the non-bonded correlation,  the nearest neighbor approximation 
is expressed in terms of the radial distribution
functions (RDFs) in the new Eqn. (21) and (22).
In example 3, a global RDF is not well defined
(because the system is inhomogeneous),
so we calculated the RDF and nearest neighbor approximation
only for the liquid phase, see the dotted line in Fig.7. By adding the
non-bonded correlation, the quality of the error estimate
is further improved.
Also the convergence with respect to
the neighboring range $R_g$ (the $r_c$ in the reviewer's comment)
is investigated (Fig.8). 
Relavant changes to the manuscript
have been made on page 9,
11 (4-th line from the bottom), 12, 29 (12-th line). All changes are marked 
in red for convenience.
\\

@@

As far as we concerned,
direct error estimates with the higher order terms are not easy.
Therefore, we investigate this issue in another way:
we compare the estimate (with bonded nearest neighbor
approximation) with the real error of the randomized COM test
(see the description of this test at the 4th line from bottom of page 28).
Since the only approximation made in the estimate is the leading order
approximation, the difference between the estimate and the real error
of randomized COM test is actually the contribution from the higher
order terms discarded by (48) and (53).
In Fig. 9-12,
we check this difference in a wide parameter range, and see in most
cases the estimate overlaps with the real error, which means
the leading order is a good approximation. 
However,
we do observe exceptions
at large $\beta$ when the grid spacing is $h=0.248\:\textsf{nm}$,
see Fig.11, and
at small $\beta$ when the interpolation order is $n=4$,
see Fig.12.
That means the higher order terms may play a role in the staggered
mesh interpolation errors. It also explains the unexpected discrepancy
between the staggered mesh ik- and analytical differentiation
at small $\beta$, $n=4$.
Relavant changes to the manuscript
have been made on page 28 (5-th line from the bottom), 32 (5-th line from the bottom).
\\

>>>>

In the revised manuscript,
we consider both of the two types of the correlations:
(1) the bonded correlation
that originates from the rigid H-O
bond and H-O-H angle within one molecule,
and (2) the
non-bonded correlation or the
intermolecular correlation that originates from
a complex coupling of various intermolecular interaction.
Estimates for the bonded correlation
have already been developed by the old manuscript,
while the non-bonded estimate
is newly added according to the reviewers' suggestion.
Please note that
both the bonded and non-bonded nearest neighbor approximations
require some uniformity of the correlation in the system:
the bonded estimate requires the uniformity of the water
direction preference (as has been discussed in the old manuscript),
while the non-bonded estimate requires the uniformity
of the density distribution and the isotropicity of the system.
Otherwise the cost of the error estimate would be $\mathcal O(N^2\log N)$.
For the non-bonded correlation,  the nearest neighbor approximation 
is expressed in terms of the radial distribution
functions (RDFs), see the new Eq. (21) and (22). In example 3, a global RDF is not well defined,
so we calculated the RDF and nearest neighbor approximation
only for the liquid phase, see the dotted line in Fig.7. By adding
the non-bonded correlation, the quality of the error estimate
is further improved.
Also the convergence with respect to
the neighboring range $R_g$ is investigated, see Fig.8.
Relevant changes to the manuscript
have been made on page 9,
11 (4-th line from the bottom), 12, 29 (12-th line). All changes are marked 
in red for convenience.
\\

@@

In the revised manuscript, the correlation error are considered
in two types: 
(1) the bonded correlation
that originates from the rigid H-O
bond and H-O-H angle within one molecule,
and (2) the
non-bonded correlation or the
intermolecular correlation that originates from
a complex coupling of various intermolecular interaction.
Estimates for the bonded correlation
have already been developed by the old manuscript,
while the non-bonded estimate
is newly developed according to the reviewers' suggestion.
Please note that
both the bonded and non-bonded nearest neighbor approximations
require some uniformity of the correlation in the system:
the bonded estimate requires the uniformity of the water
direction preference (as has been discussed in the old manuscript),
while the non-bonded estimate requires the uniformity
of the density distribution and the isotropicity of the system, which
are also the prerequisites for reducing $\rho^{(2)}$ to $g(r)$.
Otherwise the cost of the error estimate would be $\mathcal O(N^2\log N)$.
For the non-bonded correlation,  the nearest neighbor approximation 
is expressed in terms of the radial distribution
functions (RDFs) in the new Eqn. (21) and (22).
In example 3, a global RDF is not well defined
(because the system is inhomogeneous),
so we calculated the RDF and nearest neighbor approximation
only for the liquid phase, see the dotted line in Fig.7. By adding the
non-bonded correlation, the quality of the error estimate
is further improved.
Also the convergence with respect to
the neighboring range $R_g$ (the $r_c$ in the reviewer's comment)
is investigated (Fig.8). 
Relevant changes to the manuscript
have been made on page 9,
11 (4-th line from the bottom), 12, 29 (12-th line). All changes are marked 
in red for convenience.
\\

@@

As far as we concerned,
direct error estimates with the higher order terms are not easy.
Therefore, we investigate this issue in another way:
we compare the estimate (with bonded nearest neighbor
approximation) with the real error of the randomized COM test
(see the description of this test at the 4th line from bottom of page 28).
Since the only approximation made in the estimate is the leading order
approximation, the difference between the estimate and the real error
of randomized COM test is actually the contribution from the higher
order terms discarded by (48) and (53).
In Fig. 9-12,
we check this difference in a wide parameter range, and see in most
cases the estimate overlaps with the real error, which means
the leading order is a good approximation. 
However,
we do observe exceptions
at large $\beta$ when the grid spacing is $h=0.248\:\textsf{nm}$,
see Fig.11, and
at small $\beta$ when the interpolation order is $n=4$,
see Fig.12.
That means the higher order terms may play a role in the staggered
mesh interpolation errors. It also explains the unexpected discrepancy
between the staggered mesh ik- and analytical differentiation
at small $\beta$, $n=4$.
Relevant changes to the manuscript
have been made on page 28 (5-th line from the bottom), 32 (5-th line from the bottom).
\\
